Results MSRC latent class analysis

### 2021-06-07 manuscript/manuscript.Rmd
update

```{r setup, include=FALSE}
library("worcs")
source("../mplus_functions.R")
knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning = FALSE, error = TRUE)
options(knitr.kable.NA = '')
run_everything <- FALSE
```

@@

indicators <- c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", 
"CDE12", "CDE13","CDE17")

p_trans <- transformations(df[c("CDE13", "CDE17")])
# Note that due to the extreme censored nature of these variables, most variance is alreay described by a median split
props <- c(round(100*prop.table(table(df[["CDE13"]]))[1]),
           round(100*prop.table(table(df[["CDE17"]]))[1]))

@@

```{r tabcont, include = TRUE}
tab <- res_cont$lcCondMeans$overall
tab$ci1 <- tidySEM::conf_int(tab$m.1, se = tab$se.1)
tab$ci2 <- tidySEM::conf_int(tab$m.2, se = tab$se.2)
tab$CramersV <- sqrt((as.numeric(tab$chisq)/res_cont$summaries$Observations)/1)
tab$var <- rename_vars[tab$var]
tab$df <- NULL
names(tab)[1] <- "Variable"
tab <- tab[c(grep("(DV)", tab$Variable), grep("(cov)", tab$Variable)), ]
rownames(tab) <- NULL
tab <- tab[, c("Variable", "m.1", "se.1", "ci1", "m.2", "se.2", "ci2","chisq", "p")]
knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
```

@@

cats[["p 1 vs 2"]] <- NA
for(i in names(test_res)){
  #i = names(test_res)[1]
  cats$`p 1 vs 2`[grep(i, cats$Variable):(grep(i, cats$Variable) + (length(test_res[[i]])-1))] <- test_res[[i]]
}  
cats$Variable <- rename_vars[cats$Variable]
  #sapply(res_catdum, function(x){x$tests$p[1]})[match(cats$Category, dummie_dict)]
rownames(cats) <- NULL
knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")
```

>>>>

```{r setup, include=FALSE}
library("worcs")
source("../mplus_functions.R")
knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning = FALSE, error = TRUE)
options(knitr.kable.NA = '')
run_everything <- TRUE
```

@@

indicators <- c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", 
"CDE12", "CDE13","CDE17")
#df <- df[rowSums(is.na(df[, indicators])) == 0, ]
p_trans <- transformations(df[c("CDE13", "CDE17")])
# Note that due to the extreme censored nature of these variables, most variance is alreay described by a median split
props <- c(round(100*prop.table(table(df[["CDE13"]]))[1]),
           round(100*prop.table(table(df[["CDE17"]]))[1]))

@@

```{r tabcont, include = TRUE}
tab <- res_cont$lcCondMeans$overall
tab$ci1 <- tidySEM::conf_int(tab$m.1, se = tab$se.1)
tab$ci2 <- tidySEM::conf_int(tab$m.2, se = tab$se.2)
tab$CramersV <- sqrt((as.numeric(tab$chisq)/res_cont$summaries$Observations)/1)
tab$var <- rename_vars[tab$var]
tab$df <- NULL
names(tab)[1] <- "Variable"
tab <- tab[c(grep("(DV)", tab$Variable), grep("(cov)", tab$Variable)), ]
rownames(tab) <- NULL
tab <- tab[, c("Variable", "m.1", "se.1", "ci1", "m.2", "se.2", "ci2","chisq", "p")]
write.csv(tab, "classdiff_cont.csv", row.names = FALSE)
knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
```

@@

cats[["p 1 vs 2"]] <- NA
for(i in names(test_res)){
  #i = names(test_res)[1]
  cats$`p 1 vs 2`[grep(i, cats$Variable):(grep(i, cats$Variable) + (length(test_res[[i]])-1))] <- test_res[[i]]
}  
cats$Variable <- rename_vars[cats$Variable]
  #sapply(res_catdum, function(x){x$tests$p[1]})[match(cats$Category, dummie_dict)]
rownames(cats) <- NULL
write.csv(cats, "classdiff_cat.csv", row.names = FALSE)
knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")
```
